analysis-pilot

### 2023-08-15 code/analysis-pilot.Rmd
work on timing

# write_csv(here(data, 'rounds7.19.csv'))
real_offset <- raw_data
```

```{r, eval=F}
#just for pilot, need to fix offset
fix <- raw_data |> filter(trialNum==0) |> select(game, time)

real_offset <- games |> left_join(fix, by=c("gameConfig"="game")) |> mutate(offset_sec=offset_sec-time/1000)

>>>>

# write_csv(here(data, 'rounds7.19.csv'))
```

```{r}
#just for pilot, need to fix offset
#fix <- raw_data |> filter(trialNum==0) |> select(game, time)

#real_offset <- games |> left_join(fix, by=c("gameConfig"="game")) |> mutate(offset_sec=offset_sec-time/1000)

real_offset <- games
